Shallow EDSLs and Object-Oriented Programming

### 2016-06-28 paper/sections/Conclusion.tex

One limitation of the techniques presented here is that
transformations require code duplication in extensions.  For
transformations, we have to refine their return type in extensions and
supply a new implementation by duplicating the original code.  How to
define these transformations modularly, and without code duplication
is a possible line of future work.  Also, it is still tedious to
express the inheritance relationships in extensions, especially when
multiple inheritance is used. Another line of future work is to use
some meta-programming mechanisms to eliminate such boilerplate.

>>>>

One limitation of the techniques presented here is that
transformations require code duplication in extensions.  For
transformations, we have to refine their return type in extensions and
supply a new implementation by duplicating the original code. 
Though with advanced type system features of Scala, these can still be defined
modularly~\cite{zenger05independentlyextensible}, the encoding would
become significantly more complicated.
How to define these transformations modularly, without code
duplication, and without sphiticated types
is a possible line of future work.  Also, it is still tedious to
express the inheritance relationships in extensions, especially when
multiple inheritance is used. Another line of future work is to use
some meta-programming mechanisms to eliminate such boilerplate.
